---
title: "DoddFrankST"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DoddFrankST}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
knitr::opts_chunk$set(include = FALSE)
library(DoddFrankST)
library(dplyr)
```

The API is very simple: there is only one function. Its only objective is to return the results of the Dodd-Frank Act Stress Tests to the user in a format that is easy to use with other R functions.

```{r}
stress_test_results <- bank_results()
```

When in doubt about the exact definition of the variables, you can find the official data dictionary in the U.S. Board of Governors of the Federal Reserve System's (website)[https://www.federalreserve.gov/supervisionreg/files/DFAST_data_dictionary.pdf].

You can see the scenarios available (and their codes) with:
```{r}
stress_test_results %>% 
  select(scenario_id, scenario_name) %>% 
  unique()
```

For example, to plot the time series of the estimated loan loss rate for each bank under the supervisory severly adverse scenario (code = 3 as we saw above), you may use the following code:

```{r}
library(ggplot2)

stress_test_results %>% 
  filter(scenario_id == 3) %>% 
  ggplot(aes(
    x = dt_exercise_quarter, 
    y = loss_total_loan_rate, 
    color = as.factor(disclosure_legal_name))
    ) +
  geom_line(show.legend = FALSE) +
  labs(
    title = "Total projected loan loss, severely adverse scenario",
    x = "Exercise reference period",
    y = "% of projected average loans"
  ) +
  theme(legend.position = "none")
```

